Comparison with Christensen paper

### 2019-01-14 paper-comparison/compare-christensen.Rmd
Paper LDA adj v nonadj results
Adjusted v. nonadjusted data frames give qualitatively but not exactly the same results with the paper LDA

```{r adj vs non adj LDAS, eval = F}

# paper LDA w adjusted data
source('christensen-ecology-files/AIC_model_selection.R')
source('christensen-ecology-files/LDA-distance.R')

@@

# ==================================================================
# 3. run LDA model
# ==================================================================
ntopics = 4
SEED = unlist(best_seed)[1]  # For the paper, I use seed 206
ldamodel_adj = LDA(rodents[[1]],ntopics, control = list(seed = SEED),method='VEM')

plot(ldamodel_adj)

@@

plot(ldamodel_nonadj)

@@

plot(ldats_adj_lda_selected)

@@

ldats_nonadj_ldas <- LDATS::LDA_set(document_term_table = rodents$document_term_table, topics = c(2:6), nseeds = 100)
ldats_nonadj_lda_selected <- LDATS::select_LDA(LDA_models = ldats_ldas)

plot(ldats_nonadj_lda_selected)

>>>>

```{r run adj vs non adj LDAS, eval = F}
# paper LDA w adjusted data
source('christensen-ecology-files/AIC_model_selection.R')
source('christensen-ecology-files/LDA-distance.R')

@@

# choose seed with highest log likelihood for all following analyses
#    (also produces plot of community composition for 'best' run compared to 'worst')
best_seed = calculate_LDA_distance(rodents_adj[[1]],seeds_4topics)
mean_dist = unlist(best_seed)[2]
max_dist = unlist(best_seed)[3]

# ==================================================================
# 3. run LDA model
# ==================================================================
ntopics = 4
SEED = unlist(best_seed)[1]  # For the paper, I use seed 206
ldamodel_adj = LDA(rodents_adj[[1]],ntopics, control = list(seed = SEED),method='VEM')

save(ldamodel_adj, file = '~/Dropbox/ldats-models/paper_lda_adj_data.Rds')

@@

save(ldamodel_nonadj, file = '~/Dropbox/ldats-models/paper_lda_nonadj_data.Rds')

@@

save(ldats_adj_lda_selected, file = '~/Dropbox/ldats-models/ldats_lda_adj_data.Rds')

@@

ldats_nonadj_ldas <- LDATS::LDA_set(document_term_table = rodents$document_term_table, topics = c(2:6), nseeds = 100)
ldats_nonadj_lda_selected <- LDATS::select_LDA(LDA_models = ldats_nonadj_ldas)

save(ldats_nonadj_lda_selected, file = '~/Dropbox/ldats-models/ldats_lda_nonadj_data.Rds')

```{r paper adj lda}

load('~/Dropbox/ldats-models/paper_lda_adj_data.Rds')
load('~/Dropbox/ldats-models/paper_lda_nonadj_data.Rds')

# Adjusted data
plot(ldamodel_adj)

ldamodel_adj@k
```

```{r paper nonadj lda}
# Nonadjusted data
plot(ldamodel_nonadj)

ldamodel_nonadj@k

paper_gamma_comparison <- ldamodel_adj@gamma == ldamodel_nonadj@gamma
unique(paper_gamma_comparison)
